\textit{Supplementary materials for}: Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2022-12-23 paper/supplement.tex
title tweak

\title{\textit{Supplementary materials for}: Carryover clustering effects in free recall reveal how prior experiences influence memory for new experiences}
\author{Jeremy R. Manning\textsuperscript{1, *}, Andrew C. Heusser\textsuperscript{1, 2}, Kirsten Ziman\textsuperscript{1, 3},\\Emily Whitaker\textsuperscript{1}, and Paxton C. Fitzpatrick\textsuperscript{1}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Akili Interactive\\\textsuperscript{3}Princeton University\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}

\bibliographystyle{apa}

@@

\newpage
\renewcommand{\refname}{Supplementary references}
\bibliographystyle{apa}
\bibliography{cdl}

>>>>

\title{\textit{Supplementary materials for}: Carryover effects in free recall reveal how prior experiences influence memories of new experiences}
\author{Jeremy R. Manning\textsuperscript{1, *}, Andrew C. Heusser\textsuperscript{1, 2}, Kirsten Ziman\textsuperscript{1, 3},\\Emily Whitaker\textsuperscript{1}, and Paxton C. Fitzpatrick\textsuperscript{1}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Akili Interactive\\\textsuperscript{3}Princeton University\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}
\date{}

@@

\newpage
\renewcommand{\refname}{Supplementary references}
\bibliographystyle{apa}
\bibliography{CDL-bibliography/cdl}
